\section{Introduction}
% Current text-to-image (T2I) generation models~\cite{zhang2023t2i_survey,saharia2022imagen,ramesh2022dalle,podell2023sdxl,flux2024,hu2024snapgen,peebles2023dit,rombach2022high,stability2022sd21,ding2021cogview,taiyi2024} have demonstrated remarkable image synthesis capabilities, but their reliance on large parameter counts, iterative denoising, and substantial computational resources leads to prohibitively high deployment costs. Although recent on-device efforts have begun to reduce this burden~\cite{hu2024snapgen, zhao2024mobilediffusion}, native Chinese support, fully offline deployment, and training on domestic technology stacks remain underexplored. Moreover, existing T2I applications predominantly adopt a cloud-based client-server (C/S) architecture, requiring users to upload prompts and reference images to remote servers, thereby exposing sensitive data to privacy risks such as eavesdropping, unauthorized data collection, and potential breaches.
Current text-to-image (T2I) generation models~\cite{zhang2023t2i_survey,saharia2022imagen,ramesh2022dalle,podell2023sdxl,flux2024,peebles2023dit,rombach2022high,stability2022sd21,ding2021cogview,taiyi2024} have demonstrated remarkable image synthesis capabilities, but their reliance on large parameter counts, iterative denoising, and substantial computational resources leads to prohibitively high deployment costs. Recent lightweight and on-device T2I systems, such as MobileDiffusion~\cite{zhao2024mobilediffusion} and SnapGen~\cite{hu2024snapgen}, have made important progress in reducing model size and improving mobile inference efficiency. However, these efforts mainly focus on efficient model compression and deployment, while native Chinese text understanding, fully localized application scenarios, and training on domestic accelerator stacks remain underexplored. Moreover, most existing T2I applications still predominantly adopt a cloud-based client-server (C/S) architecture, requiring users to upload prompts and reference images to remote servers, thereby exposing sensitive data to privacy risks such as eavesdropping, unauthorized data collection, and potential breaches.

To address these challenges, we propose \textbf{JuZhou 1.0}, the first ultra-lightweight, native Chinese T2I foundation model supporting fully offline mobile deployment. 
% JuZhou 1.0 employs a minimalist 0.4B-parameter denoising U-Net~\cite{ho2020ddpm, rombach2022high} paired with a 1.9M-parameter distilled decoder, drastically reducing the memory footprint.
As shown in Fig.~\ref{fig:teaser}, JuZhou 1.0 employs a minimalist 0.385B-parameter denoising U-Net~\cite{ho2020ddpm, rombach2022high} paired with a 1.90M-parameter distilled decoder. Together, these two image-generation modules contain approximately 0.387B parameters, which we denote as the 0.4B JuZhou image-generation backbone for readability.
By leveraging Rectified Flow training~\cite{liu2022flow} and DMD2 distillation~\cite{yin2024improved_dmd}, we compress the inference trajectory to only four steps, enabling image generation within seconds on mobile hardware while ensuring that all user data remains processed locally.

% To train JuZhou 1.0, we constructed a large-scale 9M Chinese image-text dataset through a multi-dimensional cascaded filtering pipeline. The pipeline removes low-resolution and blurred images at the visual level, evaluates aesthetic quality and semantic alignment at the semantic level, and eliminates watermarked and unsafe content at the compliance level. This high-quality dataset enables JuZhou 1.0 to generate well-aligned, visually appealing, and safe images despite its highly compact architecture.
To train JuZhou 1.0, we constructed a large-scale 9M Chinese image-text corpus from filtered DiffusionDB prompts, Stable Diffusion 3.5 Large synthetic images, and Qwen3-based Chinese prompt translation. The original English prompts are used for image synthesis to preserve the open-domain visual distribution, and the translated Chinese prompts provide Chinese textual supervision for learning Chinese text-to-image alignment. For the poetry-oriented corpus, we further apply source-level cleaning, style augmentation, prompt-level quality control, and Qwen3-based recaptioning.

% The full training pipeline of JuZhou 1.0 was completed on Sugon K100 heterogeneous computing clusters equipped with domestic AI accelerators, without dependence on NVIDIA accelerators.
The model training and distillation pipeline of JuZhou 1.0 was completed on Sugon K100 heterogeneous computing clusters equipped with domestic AI accelerators, without dependence on NVIDIA accelerators for training. Quantitative evaluation was conducted separately in a unified NVIDIA V100 environment for fair baseline comparison.
% The cluster comprised 56 compute nodes and 224 K100 DCUs.
The main foundational training stages used 56 compute nodes with 224 K100 DCUs.
Together with the corresponding domestic software stack, this training setup demonstrates that domestic computing infrastructure can support large-scale visual generative model training and provides a practical reference for future software-hardware co-design.

On the deployment front, we completed full-stack adaptation for iOS and Android platforms. To demonstrate JuZhou 1.0's native Chinese semantic understanding, we developed and publicly released a 4-step classical Chinese poetry-to-image application, showcasing the model's ability to capture nuanced cultural contexts without relying on external translation. On a smartphone powered by the Snapdragon\textsuperscript{\textregistered} 8 Elite Gen 5 Mobile Platform, JuZhou 1.0 completes 4-step U-Net denoising in approximately 1.6 seconds, enabling high-definition image generation entirely offline.

In summary, the primary contributions of this paper are highlighted in the following five aspects:

\begin{itemize}
    \item \textbf{Ultra-Lightweight, Native Chinese T2I Model for Offline Mobile Deployment:} JuZhou 1.0 is the first native Chinese T2I foundation model purpose-built for on-device offline execution~\cite{hu2024snapgen,alibaba2020mnn,qnn}, achieving privacy-preserving local inference through 
    % a minimalist architecture consisting of a 0.4B-parameter denoising U-Net and a 1.9M-parameter distilled decoder.
    a minimalist image-generation backbone consisting of a 0.385B-parameter denoising U-Net and a 1.90M-parameter distilled decoder, totaling approximately 0.387B parameters.

    % \item \textbf{Scalable High-Quality Data Pipeline:} A multi-dimensional cascaded filtering mechanism produces a 9M high-purity Chinese image-text dataset~\cite{schuhmann2022laion,pai2023diffusion,huang2025d2c}, establishing a solid data foundation for mobile T2I scaling.
    \item \textbf{Scalable Chinese Data Construction Pipeline:} We construct a 9M general Chinese image-text corpus from filtered DiffusionDB prompts, SD3.5-Large synthetic images, and Qwen3-based prompt translation, and further build a 1.77M poem-grounded corpus through source cleaning, style-conditioned synthesis, prompt-level quality control, and recaptioning~\cite{schuhmann2022laion,pai2023diffusion,huang2025d2c}, establishing a scalable data foundation for native Chinese and poetry-oriented mobile T2I generation.

    \item \textbf{Domestic Computing Infrastructure Validation:} The full training pipeline, executed on Sugon K100 clusters, validates the feasibility of domestic hardware for large-scale generative AI training and provides a software-hardware co-design reference.

    \item \textbf{Heterogeneous Mobile Deployment:} Full-stack adaptation for both iOS and Android enables standardized edge AI deployment~\cite{alibaba2020mnn,qnn} across major mobile platforms.

    \item \textbf{Native Chinese Application:} A publicly released 4-step classical Chinese poetry-to-image application demonstrates JuZhou 1.0's ability to capture nuanced cultural contexts without external translation modules.
\end{itemize}
