% \section{Conclusion}
% We presented JuZhou 1.0, an ultra-lightweight text-to-image foundation model for fully local on-device image generation after initial model installation. 
% With a compact 0.385B-parameter denoising U-Net, a 1.9M-parameter distilled decoder, 
% 4-step distilled inference, and native Chinese semantic alignment, JuZhou 1.0 enables practical mobile deployment while preserving strong generation quality. On the Android side, the Snapdragon\textsuperscript{\textregistered}
% 8 Elite Gen 5 validation further shows that a 4-step $1024 \times 1024$
% U-Net denoising branch can be executed in approximately $1.6$~s on a
% flagship mobile SoC, while the complete poetry-to-image application remains within interactive latency under both lightweight and prompt-refinement modes. The full training pipeline was completed on domestic Sugon K100 hardware, and the model achieves a GenEval overall score of 0.69 under a unified evaluation protocol, outperforming published SD3-Medium baselines despite its much smaller denoising backbone.
% More broadly, JuZhou 1.0 validates the feasibility of a domestic training pipeline for large-scale visual generative models and highlights the practical value of lightweight on-device generation in cost, privacy, offline usability, and edge responsiveness. We hope this work provides a useful foundation for future scaling on domestic hardware, continued improvement of the domestic software stack, and real-world deployment of edge-side visual generation models.
\section{Conclusion}
We presented JuZhou~1.0, an ultra-lightweight text-to-image foundation model for fully local on-device image generation after one-time model installation. JuZhou~1.0 uses a 0.385B-parameter denoising U-Net and a 1.90M-parameter distilled decoder, forming a compact 0.387B image-generation backbone with 4-step distilled inference and direct Chinese prompting. The 28-step base model achieves a GenEval overall score of 0.69 under a unified evaluation protocol, outperforming SD3-Medium despite its substantially smaller model size. For deployment, the full poetry-to-image pipeline is validated on Android, while the core CLIP--U-Net--VAE branch is validated on iOS. On a Snapdragon\textsuperscript{\textregistered} 8 Elite Gen 5 device, the 4-step $1024 \times 1024$ U-Net denoising branch runs in approximately $1.6$~s. The model training and DMD2 step-compression pipeline was completed on domestic Sugon K100 hardware, providing a practical reference for Chinese-native generation, domestic-compute training, and edge-side visual generation.

\section*{Core Contributors}
Ce Chen, Congrui Wang, Yonglin Li, Zhenchen Wan, Mingyang Geng, Junhao Xiao, Zhengpeng Xing, Yaqing Hu, Yao Wu, Zhaoyang Qu

\section*{Contributors}
Long Lan, Xinwang Liu, Yingqi Peng, Shijia Li, Zufeng Zhang (Tsinghua University), Chen Ma (City University of Hong Kong), Jingjing Zhou (SUGON), Xingyu Wang (SUGON), Qilin Lu (SUGON), Bin Jiang (SUGON), Qilin Sun (The Chinese University of Hong Kong, Shenzhen)

\section*{Project Leaders}
Shanzhi Gu, Yaoguang Jin

\section*{Acknowledgments}
Tongliang Liu, Kede Ma, and Yifan Peng (The University of Hong Kong).

\section*{Special Acknowledgments}
JuZhou V1.0 was publicly unveiled at a launch event\footnote{\url{https://www.icswb.com/default.php?mod=live_text&live_id=914&temp=live_video}}  in Changsha, China, on May 21, 2025. The accompanying livestream attracted approximately 426,000 cumulative online views. As we prepare for the forthcoming release of JuZhou V2.0, this technical report provides a consolidated account of JuZhou V1.0, covering its design, training pipeline, deployment practice, and empirical evaluation.

We sincerely thank Sugon for its support in domestically developed AI computing infrastructure, including approximately 80 PFLOPS of K100 accelerator resources, which enabled the end-to-end training pipeline of this work. We also gratefully acknowledge support from the Hunan Provincial Key Research and Development Program under Grant No.~2025JK2146 and the Hunan Provincial College Student Entrepreneurship Investment Fund.

